---
---
title: "Lab 02 - Plastic waste"
author: "Allison Perusse"
date: "1/27/2022"
output: html_document
---
## Load packages and data

```{r setup, message=FALSE}

library(tidyverse)
library(ggplot2)
library(dplyr)
library(ggdist)
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv(here::here("data", "plastic-waste.csv"))
```

## Exercises

### Exercise 1

From these histograms, it looks like South America and Oceania have the least amount of plastic waste per capita. African and Asia have a similar amount to eachother and slightly more than Europe and North America.

```{r plastic-waste-continent}
ggplot(data = plastic_waste) + 
  aes(x = plastic_waste_per_cap, color = continent) +
  geom_histogram(binwidth = 0.2) +
  geom_density(aes(y = after_stat(count)))
  facet_wrap (~continent) 
```

### Exercise 2

```{r plastic-waste-boxplot}
ggplot(plastic_waste) +
  aes(x = continent, y = plastic_waste_per_cap, color = continent) +
  geom_boxplot()
```

```{r} 
ggplot(plastic_waste) +
  aes(x = continent, y = plastic_waste_per_cap, color = continent) +   geom_jitter(height = 0, width = .4) +
  geom_boxplot()
```

``` {r, raincloud plot}
ggplot(plastic_waste) +
  aes(x = continent,
      y = plastic_waste_per_cap, 
      fill = continent,
      color = continent) +
  geom_jitter(height = 1, width = .4) +
  geom_boxplot(color = "black",
               alpha = .5,
               width = .1,
               size = .5) +
ggdist :: stat_slab(height = .3, color = "black", size = .2, alpha = .5, position = position_nudge(y = .2 ))
```

The distribution of the data is shown better through the raincloud plot, it shows the outliers better than the box plot as well.
```
### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements


