v---
title: "board_games"
author: "Allison Perusse"
date: "4/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(viridis)
```

```{r}
ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/ratings.csv')
details <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/details.csv')
```

Joining the ratings with the details, and then using slice to only include the top 500 bayes ratings. 
```{r}
joined <- ratings |>
  left_join(details, by = "id") |>
  mutate(bayes_average = round(bayes_average, 2)) |>
  select(name, rank, yearpublished, bayes_average, users_rated, playingtime, minplayers, maxplayers)|>
  slice_max(bayes_average, n = 500)

```

Cleaning the data by filtering it to only include games published after 1800, as well as creating a column sorted by decade.
```{r}
cleaned_board_games <- joined|> 
  filter(!is.na(yearpublished), yearpublished > 1800) |>
  mutate(decade = 10 * yearpublished %/% 10) |>
  group_by(decade) |>
  na.omit()

rated_games = cleaned_board_games |> 
  filter(users_rated > 1000) |>
  select(name, decade, bayes_average)

top_5 <- rated_games |> 
  slice_max(order_by = bayes_average, n = 5, with_ties = F)
```

how the length of a board game affects their ratings
```{r}
cleaned_board_games |>
  ggplot(aes(x = playingtime, y = bayes_average,label = name, fill= as.factor(decade))) +
  geom_jitter(color = "white", pch = 21, alpha = .75, size = 3) +
  labs(fill = "Decade Published") + 
  labs(x = "Playing Time (Minutes)",
             y = "Average Bayes Rating",
        title = "Shorter Play Times Receive Higher Ratings") +
  theme(plot.background = element_rect(fill = "lavenderblush"),
        panel.background = element_rect(fill = "snow1"),
        legend.background = element_rect(fill = "lavenderblush"),
        legend.key = element_rect(fill = "lavenderblush"), 
        legend.text = element_text(color = "midnightblue", face = "bold"),
        legend.title = element_text(color = "midnightblue", face = "bold" ),
        axis.title.x = element_text(colour="midnightblue",face="bold",size=12, margin=margin(t=25)),
        axis.title.y = element_text(colour="midnightblue",face="bold",size=12, margin=margin(r=25)),
        plot.title = element_text(colour = "midnightblue", size = 15))

```
Based on the results of this plot, games with shorter play times receive higher consumer ratings. 

```{r}
top_5 |>
  group_by(decade)|>
  select(decade, name, bayes_average) |>
  mutate(index = rank(desc(bayes_average))) |>
  ggplot(aes(index, bayes_average)) +
  geom_col(aes(fill = as.factor(decade)), show.legend = F, position = 'dodge') +
  coord_flip() +
  scale_fill_brewer(palette = 18) +
  facet_wrap(~ decade, ncol = 1, strip.position = "left") +
  theme(plot.background = element_rect(fill = "gray81"),
  panel.background = element_rect(fill = "gray81"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
   labs(x = NULL, y = "Bayes Average",
       title = "Top 5 Games By Bayes Average Rating in each Decade") +
  theme(axis.text.y = element_blank(),
        strip.background = element_rect(fill = "gray75"),
        strip.text = element_text(size = rel(1.1)),
        plot.title = element_text(hjust = -0.1))
```


2010 had the highest top 5 rated games compared to the other decades.